---
title: "Homework 02"
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

```{r}
country_lists <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-09-09/country_lists.csv')
rank_by_year <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-09-09/rank_by_year.csv')

```

> Research question : How has the average number of visa-free destinations per passport changed over time in each region (2006–2025)?


```{r}
library(tidyverse)
```

```{r}
region_avg <- rank_by_year |> 
  group_by(region, year) |> 
  summarize(avg_free_visa = mean(visa_free_count, na.rm = TRUE))

ggplot(region_avg, aes(x = year, y = avg_free_visa, color = region)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_x_continuous(breaks = seq(2006, 2025, by = 2)) +
  labs(title = "Visa-Free Access by Region (2006–2025)",
       subtitle = "Average number of visa-free destinations per passport",
       x = "Year",
       y = "Average Visa-Free Count",
       color = "Region") +
  theme_minimal()
```















