---
title: "Homework 04"
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.


> Research question: Which player make the most progress on rating across August and September?


```{r}
fide_ratings_august <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-09-23/fide_ratings_august.csv')
fide_ratings_september <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-09-23/fide_ratings_september.csv')
```
```{r}
library(tidyverse)


aug <- fide_ratings_august  |> 
  arrange(id, desc(games), desc(rating))  |> 
  distinct(id, .keep_all = TRUE)

sep <- fide_ratings_september  |> 
  arrange(id, desc(games), desc(rating))  |> 
  distinct(id, .keep_all = TRUE)

fide_ratings <- fide_ratings_august |> 
  inner_join(fide_ratings_september, by = "id", suffix = c("_Aug", "_Sep")) |> 
  mutate(progress = rating_Sep - rating_Aug,
         tier  = case_when(str_detect(title_Sep, "GM|WGM") ~ "GM/WGM",
                           str_detect(title_Sep, "IM|WIM") ~ "IM/WIM",
                           str_detect(title_Sep, "FM|WFM") ~ "FM/WFM",
                           str_detect(title_Sep, "CM|WCM") ~ "CM/WCM",
                           TRUE ~ "None"),
        name = name_Sep ) |> 
  arrange(desc(progress)) |> 
  head(10)

ggplot(fide_ratings, aes(x = reorder(name, progress), y = progress, fill = tier)) +
  geom_col() +
  coord_flip() +
  scale_fill_brewer() +
  labs(title = "Top 10 Rating Improvers from August to September(2025)",
       x = "Player",
       y = "Progress on Rating") +
  theme_minimal()

```

