---
title: "Homework 05"
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

```{r}
cranes <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-09-30/cranes.csv')
```

```{r}
library(tidyverse)
library(lubridate)

cranes <- cranes %>%
  mutate(year = year(date),
         doy = yday(date),
         season = if_else(month(date) %in% 1:6, "spring", "fall")) |> 
  filter(season == "spring") |> 
  group_by(year)  |> 
  summarize(total_cranes = sum(observations, na.rm = TRUE), .groups = "drop")

ggplot(cranes, aes(x = year, y = total_cranes)) +
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "black") +
  labs(title = "Total Spring Crane Counts at Hornborgasjön by Year",
       x = "Year",
       y = "Total Observations") +
  theme_minimal()
```

