---
title: "Homework 06"
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

```{r}
euroleague_basketball <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-10-07/euroleague_basketball.csv')
```

> Research question: How are EuroLeague teams distributed across countries and how do their arena capacities compare by country?

```{r}
library(tidyverse)

euroleague_basketball |> 
  mutate(capacity_num = parse_number(Capacity)) |> 
  filter(!is.na(capacity_num)) |> 
  ggplot(aes(x = Country, y = capacity_num)) +
    geom_jitter(width = 0.2, alpha = 0.6, color = "steelblue") +
    geom_boxplot(alpha = 0.2, outlier.shape = NA) +
    coord_flip() +
    labs(title = "Distribution of Arena Capacities by Country",
         x = "Country",
         y = "Arena Capacity") +
    theme_minimal()
```

